Lightness constancy under fixed geometry

### 2017-10-11 Draft1/draft1.tex
typed linaer regression

Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the eye. These cone-responses datasets, that are labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods. We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis. These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness. Finally, we evaluate the performance of the computational methods on a test set of images.

@@

\subsection{Model of Visual System} \label{method:Isetbio}
We simulate the visual system response using isetbio software toolbox. Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics. We use the multi-spectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina. The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m. The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1. The response of the cones are measured in terms of the number of isomerizations in the cone segment ({\it over what time ??}). Since, S cones response are much lower than of L and M cones, to mdoel the amplification of the s cone response downstream, we rescale the cone response functions by the total area under the response curves. This leads to comparable number of isomerizations in the L, M and S cone on the presentation of an image. We interpolate the responses of cones in each cone class to get a 51x51 cone response image for each cone class.  Further, the three 51x51 cone response matrix corresponding to each one of the L, M and S cones are then rescaled by the mean cone response to model contrast adaption in the retina. The mean is calculated over all the 3x51x51 cones in the de-mosaic response matrix.

\subsection{Supervised Learning methods} \label{method:SupervisedLearning}
\subsubsection*{Linear Regression}
\subsubsection*{SVD regression}
\subsubsection*{Accuracy maximization analysis}

>>>>

After generating databases of labeled multi-spectral images for each one of these cases, we simulate the response of the cones in the retina cone using an accurate model of the eye. These cone-responses datasets, that are labeled with the standard lightness of the target object, are then analyzed using supervised computational learning methods.

We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis (AMA). The linear regression has been performed on the cones corresponding to the center pixel of the target object. The other two methods take the response of all the cones in the model retina. While, SVD regression a linear transformation to estimate the lightness, AMA uses a non-linear transform of the data. These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness. Finally, we evaluate the performance of the computational methods on a test set of images.

@@

\subsection{Model of Visual System} \label{method:Isetbio}
We simulate the visual system response using isetbio software toolbox. Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics. We use the multi-spectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina. The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m. The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1. The response of the cones are measured in terms of the number of isomerizations in the cone segment ({\it over what time ??}). Since, S cones response are much lower than of L and M cones, to model the amplification of the S cone response downstream, we rescale the cone response functions by the total area under the response curves. This leads to comparable number of isomerizations in the L, M and S cone on the presentation of an image. We interpolate the responses of cones in each cone class to get a $51 \times 51$ cone response image for each cone class.

The three $51 \times 51$ cone response matrix corresponding to each one of the L, M and S cones are then reshaped into a $7803 \times 1$ vector. To model the contrast adaptation in the visual system, we subtract the mean of the vector from each entry and divide by the mean. We further rescale the vector to have norm 1. The cone-response vectors corresponding to the N images for each case are concatenated into a $7803 \times N$ contrast normalized matrix $C$. The corresponding labels are represented by a $1 \times N$ row vector $Y$.

\subsection{Supervised Learning methods} \label{method:SupervisedLearning}
\subsubsection*{Linear Regression} To estimate the target object lightness using linear regression, we solve the equation $A_{(1,3)}*C_{(3,N)} = Y_{(1,N)}$. Here, $Y_{(1,N)}$ corresponds to the row vector of the lightness labels for the N images in the dataset. $C_{(3,N)}$ corresponds to the matrix of cone responses corresponding to the central pixel. Each column represents the response to one image and the rows corresponds to the contrast normalized L, M and S cone response of the center pixel. The coefficient matrix $A$ can be obtained as $A = Y*C^{-1}$.

The L, M and S response to the center pixel on the target object is calculate by taking the average of a 3x3 patch of cones near the center of the target.

\subsubsection*{SVD regression}
This 
\subsubsection*{Accuracy maximization analysis}
